Preprocessing_&_Plot_for_Moral_Categ_Replication

### 2018-12-02 Replication/Results/dataAnalysis/preproc/MS_rep_prepro.rmd
plot cross-task correlation

# write files to an upper-lelel folder
setwd(traDir)
write.csv(df.C1.V.sum_w,'MS_rep_categ_behav_wide.csv',row.names = F)
write.csv(df.C1.V.sum_noTask_w,'MS_rep_categ_behav_noTask_wide.csv',row.names = F)
write.csv(df.C1.V.sum_rt_acc_l,'MS_rep_categ__rt_acc_long.csv',row.names = F)
write.csv(df.v.sum_eff_all_w,'MS_rep_cross_taskeffect_wide.csv',row.names = F)
setwd(curDir)
```

>>>>

# write files to an upper-lelel folder
setwd(traDir)
write.csv(df.C1.V.sum_w,'MS_rep_categ_behav_wide.csv',row.names = F)
write.csv(df.C1.V.sum_noTask_w,'MS_rep_categ_behav_noTask_wide.csv',row.names = F)
write.csv(df.C1.V.sum_rt_acc_l,'MS_rep_categ__rt_acc_long.csv',row.names = F)
write.csv(df.v.sum_eff_all_w,'MS_rep_cross_taskeffect_wide.csv',row.names = F)
setwd(curDir)

# plot four scatter point.
# p1: goodself-goodother (d in matching and acc in id-based)
cor_p1 <- ggplot(df.v.sum_eff_all_w, aes(d_goodslf_goodoth, Id_ACC_goodslf_goodoth))+ 
          geom_point() + 
          labs(x = "Matching task (d prime)", y = "Identity-base Categorization task (accuracy)") +
          geom_smooth(method="lm")

# p2: goodself-goodother (RT in matching and RT in id-based)
# p3: badself-badother (d in matching and acc in id-based)
# p4: badself-badother (RT in matching and RT in id-based)
